Unemployment Effects: How Multi-Year Periods of Unemployment Influence Feelings Towards the Government

### 2020-05-08 paper.Rmd
renamed bib file

---
title: "Unemployment Effects: How Multi-Year Periods of Unemployment Influence Feelings Towards the Government"
subtitle: "GOV 1006: Paper Replication"
author: "Pieter Quinton"
date: "5/08/2020"
abstract: "Bauer (2018) finds that there is no consistent relationship between unemployment and one's trust in government or their satisfaction with democracy. I was able to completely replicate the majority of his findings aside from a summary table of the data. My extension evaluates how consistent or long-term unemployment may impact one's views. Rather than examining the effects of just a single year of unemployment, as Bauer did, I track unemployement trends over longer periods of time to see if extended periods of unemployment have a stronger impact on one's feelings towards the government and its institutions than shorter periods of unemployment do."
header-includes:
    - \usepackage{setspace}\doublespacing
output: 
  bookdown::pdf_document2:
    keep_tex: true
    toc: no
document_class: article
bibliography: milestone5_bib.bib
mainfont: Wingdings
sansfont: Wingdings
fontsize: 12pt
---

>>>>

---
title: "Unemployment Effects: How Multi-Year Periods of Unemployment Influence Feelings Towards the Government"
subtitle: "GOV 1006: Paper Replication"
author: "Pieter Quinton"
date: "5/08/2020"
abstract: "Bauer (2018) finds that there is no consistent relationship between unemployment and one's trust in government or their satisfaction with democracy. I was able to completely replicate the majority of his findings aside from a summary table of the data. My extension evaluates how consistent or long-term unemployment may impact one's views. Rather than examining the effects of just a single year of unemployment, as Bauer did, I track unemployement trends over longer periods of time to see if extended periods of unemployment have a stronger impact on one's feelings towards the government and its institutions than shorter periods of unemployment do."
header-includes:
    - \usepackage{setspace}\doublespacing
output: 
  bookdown::pdf_document2:
    keep_tex: true
    toc: no
document_class: article
bibliography: bibliography.bib
mainfont: Wingdings
sansfont: Wingdings
fontsize: 12pt
---
